---
title: "Duke Update"
author: "Jacob Ford DCHC MPO"
date: "3/3/2021"
output: html_document
---



For Duke University, a 2015 inventory of parking spaces was used to update the base year. Besides the base year data changing the methods are the same as completed in the Durham update. Future projections are based off employment growth and the distribution from the Work, Visitor and University categories to trip purposes is based off peak trip attraction share.



```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
##devtools::install_github("wsp-sag/tcadr")
##install.packages('htmltools')
library(tcadr)
library(DT)

##read_tcad("inst/extdata/TransitR.bin")

##https://github.com/wsp-sag/tcadr


SE_2013 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/SE_2013-rev.bin")
SE_2016<- tcadr::read_tcad ("SE_2016.BIN")


SE_2025 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM SE Data Inputs/2025/SE_2025.bin")

SE_2045 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM SE Data Inputs/2045/SE_2045.bin")



Stud_Off_2045 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2045 MTP wAmendments/Input/Univ/Stud_Off Total 2045.bin")


Stud_Off_2016 <- tcadr::read_tcad("Stud_Off Total 2016.bin")
library(dplyr)

SE_2025_sum <- SE_2025 %>%
  group_by(PASA) %>%
  summarize(n = n(),
            work = sum(Industry + Office + Service_RateLow + Service_RateHigh + Retail),
            vistor = sum(Service_RateLow + Service_RateHigh + Retail))


SE_2045_sum <- SE_2045 %>%
  group_by(PASA) %>%
  summarize(n = n(),
            work = sum(Industry + Office + Service_RateLow + Service_RateHigh + Retail),
            vistor = sum(Service_RateLow + Service_RateHigh + Retail))

SE_2016_sum <- SE_2016 %>%
  group_by(PASA) %>%
  summarize(n = n(),
            work = sum(Industry + Office + Service_RateLow + Service_RateHigh + Retail),
            vistor = sum(Service_RateLow + Service_RateHigh + Retail))

SE_2045_sum$University <- NA

SE_2045_sum$University[2] <- sum(Stud_Off_2045$UNC)
SE_2045_sum$University[3] <- sum(Stud_Off_2045$DUKE)
SE_2045_sum$University[4] <- sum(Stud_Off_2045$NCSU)
SE_2045_sum$University[5] <- sum(Stud_Off_2045$NCCU)

SE_2016_sum$University <- NA

SE_2016_sum$University[2] <- sum(Stud_Off_2016$UNC)
SE_2016_sum$University[3] <- sum(Stud_Off_2016$DUKE)
SE_2016_sum$University[4] <- sum(Stud_Off_2016$NCSU)
SE_2016_sum$University[5] <- sum(Stud_Off_2016$NCCU)

SE_2016_sum=SE_2016_sum[-1,]




###Add Park Capcity files
ParkCap_2013 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2013 Base Year/Input/Programs/Parkcap.bin")
ParkCap_2016 <- tcadr::read_tcad("C:/Users/JacobFo/TRMv6.2/Original TRMv6.2_2016/Input/Programs/Parkcap.bin")
ParkCap_2025 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2025 MTP wAmendments/Input/Programs/Parkcap.bin")
ParkCap_2035 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2035 MTP wAmendments/Input/Programs/Parkcap.bin")
ParkCap_2045 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2045 MTP wAmendments/Input/Programs/Parkcap.bin")

ParkCap_2013$Year <- 2013
ParkCap_2016$Year <- 2016
ParkCap_2025$Year <- 2025
ParkCap_2035$Year <- 2035
ParkCap_2045$Year <- 2045

All_Caps <- rbind(ParkCap_2013, ParkCap_2016, ParkCap_2025, ParkCap_2035, ParkCap_2045)
library(readxl)
parkingspaces <-read_excel("parkingspaces.xlsx")
```

Duke's Annual Employment Growth Rate:

Duke's Visitor (Retail + Service) Growth Rate: 

Duke's University Employment Growth Rate: 

```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
duke_emp_growth<-log((SE_2045_sum$work[SE_2045_sum$PASA==2])/(SE_2016_sum$work[SE_2016_sum$PASA==2]))/(2045-2016)
duke_visitor_growth<-log((SE_2045_sum$vistor[SE_2045_sum$PASA==2])/(SE_2016_sum$vistor[SE_2016_sum$PASA==2]))/(2045-2016)
duke_uni_growth<-log((SE_2045_sum$University[SE_2045_sum$PASA==2])/(SE_2016_sum$University[SE_2016_sum$PASA==2]))/(2045-2016)

duke_emp_growth
duke_visitor_growth
duke_uni_growth

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
duke <- data.frame(matrix(ncol =7, nrow = 6))
t <- c("Year", "Work Spaces", "Visitor Spaces", "University Spaces", "Total Spaces" ,"Capacity Uses", "Capacity Total")
colnames(duke) <- t

years_2 <-c(2013, 2015, 2020, 2030, 2040, 2050) 

duke$Year <- years_2

duke$`Work Spaces`[1]<- parkingspaces$Work[parkingspaces$PASA== "2 = Duke Campus" & parkingspaces$Year==2013]
duke$`Visitor Spaces`[1]<- parkingspaces$Visitors[parkingspaces$PASA== "2 = Duke Campus" & parkingspaces$Year==2013]
duke$`University Spaces`[1]<- parkingspaces$Uni[parkingspaces$PASA== "2 = Duke Campus" & parkingspaces$Year==2013]

duke$`Capacity Total`[1] <-ParkCap_2013$CapHBW[ParkCap_2013$PASA==2] + ParkCap_2013$CapHBSH[ParkCap_2013$PASA==2] + ParkCap_2013$CapHBO[ParkCap_2013$PASA==2 ]+ ParkCap_2013$CapHBU[ParkCap_2013$PASA==2]+ ParkCap_2013$CapNHNW[ParkCap_2013$PASA==2] +ParkCap_2013$CapWBNH[ParkCap_2013$PASA==2]

duke$`Total Spaces`[duke$Year==2015] <- 21064

duke$`Total Spaces`[duke$Year==2013] <- duke$`Work Spaces`[duke$Year==2013]+ duke$`Visitor Spaces`[duke$Year==2013] + duke$`University Spaces`[duke$Year==2013]
duke$`Work Spaces`[duke$Year==2015] <- duke$`Total Spaces`[duke$Year==2015] *( duke$`Work Spaces`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013])
duke$`Visitor Spaces`[duke$Year==2015] <- duke$`Total Spaces`[duke$Year==2015] *( duke$`Visitor Spaces`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013])
duke$`University Spaces`[duke$Year==2015] <- duke$`Total Spaces`[duke$Year==2015] *( duke$`University Spaces`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013])

duke


```



```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
##forecastING 

duke$`Work Spaces`[duke$Year==2020] <-duke$`Work Spaces`[duke$Year==2015]*(1+duke_emp_growth)^(2020-2015)
duke$`Work Spaces`[duke$Year==2030] <-duke$`Work Spaces`[duke$Year==2015]*(1+duke_emp_growth)^(2030-2015)
duke$`Work Spaces`[duke$Year==2040] <-duke$`Work Spaces`[duke$Year==2015]*(1+duke_emp_growth)^(2040-2015)
duke$`Work Spaces`[duke$Year==2050] <-duke$`Work Spaces`[duke$Year==2015]*(1+duke_emp_growth)^(2050-2015)

duke$`Visitor Spaces`[duke$Year==2020] <-duke$`Visitor Spaces`[duke$Year==2015]*(1+duke_visitor_growth)^(2020-2015)
duke$`Visitor Spaces`[duke$Year==2030] <-duke$`Visitor Spaces`[duke$Year==2015]*(1+duke_visitor_growth)^(2030-2015)
duke$`Visitor Spaces`[duke$Year==2040] <-duke$`Visitor Spaces`[duke$Year==2015]*(1+duke_visitor_growth)^(2040-2015)
duke$`Visitor Spaces`[duke$Year==2050] <-duke$`Visitor Spaces`[duke$Year==2015]*(1+duke_visitor_growth)^(2050-2015)

duke$`University Spaces`[duke$Year==2020] <-duke$`University Spaces`[duke$Year==2015]*(1+duke_uni_growth)^(2020-2015)
duke$`University Spaces`[duke$Year==2030] <-duke$`University Spaces`[duke$Year==2015]*(1+duke_uni_growth)^(2030-2015)
duke$`University Spaces`[duke$Year==2040] <-duke$`University Spaces`[duke$Year==2015]*(1+duke_uni_growth)^(2040-2015)
duke$`University Spaces`[duke$Year==2050] <-duke$`University Spaces`[duke$Year==2015]*(1+duke_uni_growth)^(2050-2015)




duke$`Total Spaces`<- duke$`Work Spaces`+duke$`Visitor Spaces`+duke$`University Spaces`



```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
duke$`Capacity Total`[duke$Year==2015]<-duke$`Capacity Total`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013] * duke$`Total Spaces`[duke$Year==2015]
duke$`Capacity Total`[duke$Year==2020]<-duke$`Capacity Total`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013] * duke$`Total Spaces`[duke$Year==2020]
duke$`Capacity Total`[duke$Year==2030]<-duke$`Capacity Total`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013] * duke$`Total Spaces`[duke$Year==2030]
duke$`Capacity Total`[duke$Year==2040]<-duke$`Capacity Total`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013] * duke$`Total Spaces`[duke$Year==2040]
duke$`Capacity Total`[duke$Year==2050]<-duke$`Capacity Total`[duke$Year==2013]/duke$`Total Spaces`[duke$Year==2013] * duke$`Total Spaces`[duke$Year==2050]

duke$`Capacity Uses` <- duke$`Capacity Total`/2
duke[,-1] <- round(duke[,-1], digits=0)


```

Using the updated 2015 inventory as the base year for 2015, after removing parking spaces outside of Duke's PASA, the total number of parking spaces is **21,064**. This is entered into teh table below, along with the original base year of 2013 which was used for the calculation of 2025, 2035, and 2045 parking data. 

To calculate worker, visitor and university spaces, the proportion from 2013 is kept constant in the new base year 2015 scenario. Similarly, the ratio of capacity to spaces in 2013 is kept constant in 2015. 

The future years are calculated based off the employment growth in the PASA for workers spaces (total employment), visitor spaces (retail + service) and university spaces (university employees). Annual growth rates are seen below: 

```{r, echo=FALSE, message=FALSE}
duke_emp_growth<-log((SE_2045_sum$work[SE_2045_sum$PASA==2])/(SE_2016_sum$work[SE_2016_sum$PASA==2]))/(2045-2016)
duke_visitor_growth<-log((SE_2045_sum$vistor[SE_2045_sum$PASA==2])/(SE_2016_sum$vistor[SE_2016_sum$PASA==2]))/(2045-2016)
duke_uni_growth<-log((SE_2045_sum$University[SE_2045_sum$PASA==2])/(SE_2016_sum$University[SE_2016_sum$PASA==2]))/(2045-2016)

duke_emp_growth
duke_visitor_growth
duke_uni_growth

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
duke <- add_row(duke)
duke$Year[7]<-"2045 Original"

duke <- add_row(duke)
duke$Year[8]<-"2016 Original"

duke$`Work Spaces`[7] <- parkingspaces$Work[parkingspaces$PASA=="2 = Duke Campus" & parkingspaces$Year==2045]
duke$`University Spaces`[7] <- parkingspaces$Uni[parkingspaces$PASA=="2 = Duke Campus" & parkingspaces$Year==2045]
duke$`Visitor Spaces`[7] <- parkingspaces$Visitors[parkingspaces$PASA=="2 = Duke Campus" & parkingspaces$Year==2045]
duke$`Capacity Total`[7] <- ParkCap_2045$CapHBW[ParkCap_2045$PASA==2] + ParkCap_2045$CapHBO[ParkCap_2045$PASA==2]+ ParkCap_2045$CapHBSH[ParkCap_2045$PASA==2]+ ParkCap_2045$CapNHNW[ParkCap_2045$PASA==2]+ ParkCap_2045$CapWBNH[ParkCap_2045$PASA==2]+ ParkCap_2045$CapHBU[ParkCap_2045$PASA==2]

duke$`Work Spaces`[8] <- parkingspaces$Work[parkingspaces$PASA=="2 = Duke Campus" & parkingspaces$Year==2016]
duke$`University Spaces`[8] <- parkingspaces$Uni[parkingspaces$PASA=="2 = Duke Campus" & parkingspaces$Year==2016]
duke$`Visitor Spaces`[8] <- parkingspaces$Visitors[parkingspaces$PASA=="2 = Duke Campus" & parkingspaces$Year==2016]
duke$`Capacity Total`[8] <- ParkCap_2016$CapHBW[ParkCap_2016$PASA==2] + ParkCap_2016$CapHBO[ParkCap_2016$PASA==2]+ ParkCap_2016$CapHBSH[ParkCap_2016$PASA==2]+ ParkCap_2016$CapNHNW[ParkCap_2016$PASA==2]+ ParkCap_2016$CapWBNH[ParkCap_2016$PASA==2]+ ParkCap_2016$CapHBU[ParkCap_2016$PASA==2]



duke$`Total Spaces`<- duke$`Work Spaces`+duke$`Visitor Spaces`+duke$`University Spaces`
duke$`Capacity Uses` <- duke$`Capacity Total`/2

duke[,-1] <- round(duke[,-1], digits=0)
datatable(duke)
```


**Trips Attracted to Durham from TRMv6.2 2016 input. **



```{r, echo=FALSE, message=FALSE, warning=FALSE}

duke_attractions <- data.frame(matrix(ncol =6, nrow = 1))
dukenames <- c("HBW", "HBShop", "HBO", "WBNH", "NHNW", "Total")
colnames(duke_attractions) <- dukenames





duke_attractions$HBW<-sum(PK_HBW$A[PK_HBW$PASA==2])
duke_attractions$HBShop<-sum(PK_SHP$A[PK_SHP$PASA==2])
duke_attractions$HBO<-sum(PK_HBO$A[PK_HBO$PASA==2])
duke_attractions$WBNH<-sum(PK_WBNH$A[PK_WBNH$PASA==2])
duke_attractions$NHNW<-sum(PK_NHNW$A[PK_NHNW$PASA==2])

duke_attractions$Total<-duke_attractions$HBW+
  duke_attractions$HBShop+
  duke_attractions$HBO+
  duke_attractions$WBNH+
  duke_attractions$NHNW

duke_attractions <-round(duke_attractions,digits=0)
datatable(duke_attractions)
  

```





