---
title: "Parking Capacity Overview"
output: html_document
---




Parking capacity is a composite measurement of the total supply of parking spaces and is measured by PASA type and trip purpose. It has previously been calculated as a function of the base year (2013) and future scenario year parking spaces, current and future number of employee/enrollee in the PASA, and vehicles parked per space. The base year for the parking spaces is 2013, therefore all parking capacity below is based off 2013 data. Growth factors based off the employment growth for Workers (Total Employment), Visitors (Retail + Visitors) and University (Off-Campus Students). These were used to extend the 2013 base year to 2025-2035-2045 scenarios. Parking Capacity Data is sourced from the ParkCap.bin file in the respective model scenario year 'Programs' folder within from the TRMv6.2 official svn repository.  


**Original Data Sources on ITRE Drive**

[2013 Source '2013_ParkCapBin' tab](https://docs.google.com/spreadsheets/d/1V8ewuzEgoqsqsj58juQLqc4XfVYAYUCc/edit#gid=1481906281 "2013 Calculation")

[2013 Durham CBD Source 'TRMv6_Cap' tab Approach C](https://docs.google.com/spreadsheets/d/1GBQPYtD1S72zwLNfarZvMwUcQRPTBGY6/edit#gid=1143785036 "2013 Durham Calculation")

[2016 Source 'Cap_2016 Tab'](https://docs.google.com/spreadsheets/d/10gmqbC3IzuMr70pT1adIl_eRlYauPS2T/edit#gid=322186100 "2016 Calculation")

[2025 Source 'Cap_E' Tab, Approach E](https://docs.google.com/spreadsheets/d/1WBSfRdTZsmZuUM5loBz3phY5CECVBygo/edit#gid=1258207298 "2025 Calculation")

[2035 Source 'Cap_'E Tab, Approach E](https://docs.google.com/spreadsheets/d/1ucD5uRabUwJ4egfoXGO06EfKNyRHBWKH/edit#gid=774690020 "2035 Calculation")

[2045 Source 'Cap_E' Tab, Approach E+](https://docs.google.com/spreadsheets/u/1/d/1Jc5vPo6ptHY3e3eU5rqNzr4y0tUI6p-q/edit?usp=drive_web&ouid=116527721669642028928&rtpof=true "2045 Calculation")

```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
library(xlsx)
library(readxl)
library(plotly)
library(sf)
library(dplyr)
library(tidygeocoder)
library(leaflet)
library(rgdal)
library(dplyr)
library(rmarkdown)
library(crosstalk)
library(lubridate)
library(htmltools)
library(remotes)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
##devtools::install_github("wsp-sag/tcadr")
##install.packages('htmltools')
library(tcadr)

##read_tcad("inst/extdata/TransitR.bin")

##https://github.com/wsp-sag/tcadr


SE_2013 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/SE_2013-rev.bin")
SE_2016<- tcadr::read_tcad ("SE_2016.BIN")


SE_2025 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM SE Data Inputs/2025/SE_2025.bin")

SE_2045 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM SE Data Inputs/2045/SE_2045.bin")



Stud_Off_2045 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2045 MTP wAmendments/Input/Univ/Stud_Off Total 2045.bin")


Stud_Off_2016 <- tcadr::read_tcad("Stud_Off Total 2016.bin")
library(dplyr)

SE_2025_sum <- SE_2025 %>%
  group_by(PASA) %>%
  summarize(n = n(),
            work = sum(Industry + Office + Service_RateLow + Service_RateHigh + Retail),
            vistor = sum(Service_RateLow + Service_RateHigh + Retail))


SE_2045_sum <- SE_2045 %>%
  group_by(PASA) %>%
  summarize(n = n(),
            work = sum(Industry + Office + Service_RateLow + Service_RateHigh + Retail),
            vistor = sum(Service_RateLow + Service_RateHigh + Retail))

SE_2016_sum <- SE_2016 %>%
  group_by(PASA) %>%
  summarize(n = n(),
            work = sum(Industry + Office + Service_RateLow + Service_RateHigh + Retail),
            vistor = sum(Service_RateLow + Service_RateHigh + Retail))

SE_2045_sum$University <- NA

SE_2045_sum$University[2] <- sum(Stud_Off_2045$UNC)
SE_2045_sum$University[3] <- sum(Stud_Off_2045$DUKE)
SE_2045_sum$University[4] <- sum(Stud_Off_2045$NCSU)
SE_2045_sum$University[5] <- sum(Stud_Off_2045$NCCU)

SE_2016_sum$University <- NA

SE_2016_sum$University[2] <- sum(Stud_Off_2016$UNC)
SE_2016_sum$University[3] <- sum(Stud_Off_2016$DUKE)
SE_2016_sum$University[4] <- sum(Stud_Off_2016$NCSU)
SE_2016_sum$University[5] <- sum(Stud_Off_2016$NCCU)

SE_2016_sum=SE_2016_sum[-1,]




###Add Park Capcity files
ParkCap_2013 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2013 Base Year/Input/Programs/Parkcap.bin")
ParkCap_2016 <- tcadr::read_tcad("C:/Users/JacobFo/TRMv6.2/Original TRMv6.2_2016/Input/Programs/Parkcap.bin")
ParkCap_2025 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2025 MTP wAmendments/Input/Programs/Parkcap.bin")
ParkCap_2035 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2035 MTP wAmendments/Input/Programs/Parkcap.bin")
ParkCap_2045 <- tcadr::read_tcad("C:/Users/JacobFo/OneDrive - City of Durham/MTP Work/TRM MTP Inputs Scenario Years/2045 MTP wAmendments/Input/Programs/Parkcap.bin")

ParkCap_2013$Year <- 2013
ParkCap_2016$Year <- 2016
ParkCap_2025$Year <- 2025
ParkCap_2035$Year <- 2035
ParkCap_2045$Year <- 2045

All_Caps <- rbind(ParkCap_2013, ParkCap_2016, ParkCap_2025, ParkCap_2035, ParkCap_2045)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

labels = c("1 = UNC Campus",
"2 = Duke Campus",
"3 = NCSU Campus",
"4 = NCCU Campus",
"5 = Chapel Hill CBD",
"6 = Durham CBD",
"7 = Raleigh CBD",
"8 = Carrboro CBD",
"9 = Hillsborough CBD",
"10=RDU"


)

levels = c(1,2,3,4,5,6,7,8,9,10)

All_Caps$PASA <- ordered(All_Caps$PASA,
                         levels=levels,
                         labels=labels)

library(lubridate)

lubridate::ymd(All_Caps$Year, truncated=2L)

```


\br
\br




**Parking Capacity Datatable: **



```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(DT)
datatable(All_Caps, filter='top',
          caption="Parking Capacities for PASAs for 2013, 2016, 2025, 2035 and 2045")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
All_Caps$Tot_Cap <- All_Caps$CapHBW + All_Caps$CapHBO + All_Caps$CapHBSH + All_Caps$CapHBU + All_Caps$CapNHNW + All_Caps$CapWBNH 
```

**Interactive Bar Charts**

*Double click on a PASA to isolate in the graph*

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
library(plotly)

bars <- plot_ly(All_Caps, x = ~Year, y=~Tot_Cap, type='bar', name='Total Capacity', hoverinfo='text', text = ~paste(PASA, 
                                                                                                                    '</br></br>', Tot_Cap))
  
bars <- bars %>%
  add_trace(y=~CapHBW, name = 'HBW', hoverinfo='text', text = ~paste(PASA,'</br></br>', CapHBW)) %>%
  add_trace(y=~CapHBO, name = 'HBO', hoverinfo='text', text = ~paste(PASA,'</br></br>', CapHBO)) %>%
  add_trace(y=~CapHBSH, name = 'HBSH', hoverinfo='text', text = ~paste(PASA,'</br></br>', CapHBSH)) %>%
  layout(title="Parking Capacity",
         barmode='group',
         xaxis=list(type="category"))

bars

```



**Total Capacity**

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
total_bar <- plot_ly(All_Caps, x=~Year, y=~Tot_Cap, type='bar', color=~PASA, colors="Accent", hoverinfo='text', text = ~paste(PASA,'</br></br>', Tot_Cap)) %>%
  layout(barmode='group',
         xaxis=list(type="category"))

total_bar
```









**HBW Capacity**

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
hbw_bar <- plot_ly(All_Caps, x=~Year, y=~CapHBW, type='bar', color=~PASA, colors="Accent", hoverinfo='text', text = ~paste(PASA,'</br></br>', CapHBW)) %>%
  layout(barmode='group',
         xaxis=list(type="category"))

hbw_bar
```








**HBO Capacity**

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
hbo_bar <- plot_ly(All_Caps, x=~Year, y=~CapHBO, type='bar', color=~PASA, colors="Accent", hoverinfo='text', text = ~paste(PASA,'</br></br>', CapHBO)) %>%
  layout(barmode='group',
         xaxis=list(type="category"))

hbo_bar
```





**HBSH Capacity**

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
hbsh_bar <- plot_ly(All_Caps, x=~Year, y=~CapHBSH, type='bar', color=~PASA, colors="Accent", hoverinfo='text', text = ~paste(PASA,'</br></br>', CapHBSH)) %>%
  layout(barmode='group',
         xaxis=list(type="category"))

hbsh_bar
```


**HBU Capacity**

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
hbu_bar <- plot_ly(All_Caps, x=~Year, y=~CapHBU, type='bar', color=~PASA, colors="Accent", hoverinfo='text', text = ~paste(PASA,'</br></br>', CapHBU)) %>%
  layout(barmode='group',
         xaxis=list(type="category"))

hbu_bar
```



**NHNW Capacity**

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
nhnw_bar <- plot_ly(All_Caps, x=~Year, y=~CapNHNW, type='bar', color=~PASA, colors="Accent", hoverinfo='text', text = ~paste(PASA,'</br></br>', CapNHNW)) %>%
  layout(barmode='group',
         xaxis=list(type="category"))

nhnw_bar
```


**WBNH Capacity**

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
wbnh_bar <- plot_ly(All_Caps, x=~Year, y=~CapWBNH, type='bar', color=~PASA, colors="Accent", hoverinfo='text', text = ~paste(PASA,'</br></br>', CapWBNH)) %>%
  layout(barmode='group',
         xaxis=list(type="category"))

wbnh_bar
```






